Malacology: A Programmable Storage System

### 2016-10-09 paper/paper.tex
sty: setup eurosys latex style
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>
paper: started fixing table
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\documentclass[10pt,twocolumn]{article}

\usepackage{fullpage}
\usepackage{times}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{amsmath}
\usepackage{mathptmx}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

\usepackage{graphicx}
\usepackage[font=footnotesize,labelfont=bf]{caption}
\usepackage{pstricks}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,keepaspectratio}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Malacology: A Programmable Storage System},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
%\setlength{\parindent}{0pt}
%\setlength{\parskip}{6pt plus 2pt minus 1pt}
%\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{5}

\title{Malacology: A Programmable Storage System}
\author{Paper \# 123}
\date{}
\begin{document}

@@

@@

\label{services}
\begin{table}
\centering
\begin{tabular}{  l | l | l | l }
\textbf{Service} & \text{*} & \textbf{Malacology Collection of Interfaces/APIS}       & \textbf{Used to...}  \\ \hline
Mantle           &          & Load Balancing      & load balance metadata \\
                 & \cmark   & Versioning          & agree on current balancer \\ 
                 & \cmark   & Batching            & control client write lock \\
                 &          & Durability          & persist policy logic \\\hline
ZLog             & \cmark   & Logical Device      & implement CORFU \\ 
                 & \cmark   & Versioning          & install ZLog interfaces \\
                 &          & Durability          & persist log entries \\ \hline
ZLog             &          & Load balancing      & load balance sequencers \\
Seqr.            & \cmark   & Batching            & guard shared resource \\ %\hline
                 %\multicolumn{4}{c}{} \\ 
                 %\multicolumn{4}{c}{\#: interface in metadata server,     \(\mp\): interface in object storage server} \\ 
\end{tabular}
\caption{Mantle and ZLog are built using Malacology hooks so they inherit the
robustness of the subsystems of the underlying stack. For the \text{*} column,
the \cmark s are hooks contributed in this paper; durability is already
provided with a client library and the MDS Logical Device is already
published~\cite{sevilla:sc15-mantle}. }
\label{table:implementation}
\end{table}

>>>>

%\documentclass[10pt,twocolumn]{article}
\documentclass[preprint]{sigplanconf-eurosys}

%\usepackage{fullpage}
%\usepackage{times}
\usepackage{multirow}
\usepackage{arydshln}
%\usepackage{amssymb,amsmath}
%\usepackage{ifxetex,ifluatex}
\usepackage{amsmath}
%\usepackage{mathptmx}
\usepackage{graphicx}
\usepackage{listings}
%\usepackage{amssymb}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}%
%\newcommand{\xmark}{\ding{55}}%
%
%
%
%% use upquote if available, for straight quotes in verbatim environments
%\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
%
%\usepackage[font=footnotesize,labelfont=bf]{caption}
\usepackage{pstricks}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
%% Scale images if necessary, so that they will not overflow the page
%% margins by default, and it is still possible to overwrite the defaults
%% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,keepaspectratio}

\usepackage[unicode=true]{hyperref}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Malacology: A Programmable Storage System},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
%%\setlength{\parindent}{0pt}
%%\setlength{\parskip}{6pt plus 2pt minus 1pt}
%%\setlength{\emergencystretch}{3em}  % prevent overfull lines
%\setcounter{secnumdepth}{5}

\title{Malacology: A Programmable Storage System}
\authorinfo{Paper ID: 123}
           {Total Page: 12}
\date{}
\begin{document}

@@

\begin{table*}
\centering
\begin{tabular}{  l | l | l | l | l}
\textbf{Interface}            &
\textbf{\text{*}}             &
\textbf{Provides...}          &
\textbf{Example in Storage} & \\ \hline
Load Balancing  & migration \& monitoring primitives   & \\
Versioning      & consistency primitives               & \\ 
Shared Resource & serialization \& batching primitives
                & \\
Durability      & persistence primitives
                & \\
Logical Device  & transaction \& atomicity primitives 
                & Swift/ZeroVM in situ storage \& compute [1] \\ 
\end{tabular}
\caption{The Malacology interfaces are commonly used abstractions used
internally in storage stacks.}
\label{table:implementation}
\end{table*}
% http://www.zerovm.org/zerocloud.html

@@

\label{services}
\begin{table}
\centering
\begin{tabular}{  l | l | l | l}
\textbf{Service}              &
\textbf{Used to...}           &
\textbf{Malacology Interface} & \\ \hline
Mantle & load balance metadata     & Load Balancing  \\
       & agree on current balancer & Versioning      \\ 
       & control client write lock & Shared Resource \\
       & persist policy logic      & Durability      \\ \hline
ZLog   & implement CORFU           & Logical Device  \\ 
       & install ZLog interfaces   & Versioning      \\
       & persist log entries       & Durability      \\ \hline
ZLog   & load balance sequencers   & Load Balancing  \\
Seqr.  & guard shared resource     & Shared Resource \\ 
\end{tabular}
\caption{Mantle and ZLog are built using Malacology interfaces so they inherit the
robustness of the subsystems of the underlying stack. The \cmark s are
interfaces contributed in this paper; durability is already provided with a
client library and the MDS Logical Device is already
published~\cite{sevilla:sc15-mantle}. }
\label{table:implementation}
\end{table}
